\documentclass{resume}
\usepackage[hidelinks]{hyperref}

% Compact lists
\usepackage{enumitem}
\setlist[itemize]{itemsep=2pt, topsep=2pt, parsep=0pt, partopsep=0pt}

\begin{document}
\begin{center}
    \textbf{\Huge Diego Cicotoste} \\[1pt]
    \small
    305-988-8058 $|$
    \href{mailto:cicotosted@gmail.com}{\underline{cicotosted@gmail.com}} $|$
    \href{https://www.diegocico.com}{\underline{diegocico.com}} $|$
    \href{https://linkedin.com/in/diego-cicotoste}{\underline{linkedin.com/in/diego-cicotoste}}
\end{center}

% =======================
% Education
% =======================
\section{Education}
\textbf{Bachelor of Science in Computer Science}, Northeastern University
\hfill \textbf{Sept 2023 – Jun 2026}\\
\textbf{Study Abroad}: London

% =======================
% Experience
% =======================
\section{Experience}

\textbf{Software Development Engineering Intern} \hfill \textbf{May 2025 – Aug 2025}\\
Amazon \hfill \textit{Boston, MA}
\begin{itemize}
    \item Built a \textbf{scalable GenAI system} to extract and import contracts, reducing manual effort by \textbf{80\%} and cutting processing time from \textbf{3 hours to under 2 minutes}.
    \item Developed a \textbf{secure React frontend} with \textbf{SSO/Federate login} and a \textbf{Lambda-based backend} using \textbf{Bedrock, Glue, S3, DynamoDB}; handled \textbf{hundreds of contracts/month}.
\end{itemize}

\textbf{Data Product Manager} \hfill \textbf{Sept 2024 – Apr 2025}\\
Supply Trace \hfill \textit{Boston, MA}
\begin{itemize}
    \item Managed a \textbf{team of 3 developers}, improving sprint velocity with tighter scoping and tracking.
    \item Designed algorithms to process and merge \textbf{millions of data points/month}, improving reliability and throughput.
    \item Rebuilt \textbf{ingestion pipelines} with safer deploys and monitoring, reducing ETL latency by \textbf{50\%}.
\end{itemize}

\textbf{Software Development Engineering Intern} \hfill \textbf{May 2024 – Aug 2024}\\
Amazon \hfill \textit{Dallas, TX}
\begin{itemize}
    \item Extracted and processed data from \textbf{2M+ users} via \textbf{Productiv API}, unlocking better product insights.
    \item Built dashboards in \textbf{Amazon QuickSight}, increasing stakeholder visibility and contributing to \textbf{\$10M} in cost reductions.
\end{itemize}

\textbf{Manager} \hfill \textbf{Jun 2021 – Aug 2023}\\
Code Ninjas Aventura \hfill \textit{Miami, FL}
\begin{itemize}
    \item Oversaw \textbf{15 instructors}, managing ops/training/scheduling for \textbf{100+ students}.
    \item Grew revenue to \textbf{\$30,000+ monthly}, peaking at \textbf{\$70,000+} during summer camps.
\end{itemize}

% =======================
% Projects
% =======================
\section{Projects}

\textbf{TwoPix (Private Photo Messaging App)} $|$ SwiftUI, Firebase
\begin{itemize}
    \item Built a gesture-driven photo messaging app for two users with \textbf{pinch, swipe, and double-tap} interactions.
    \item Implemented secure pairing via a “\textbf{Pix Code},” real-time chat sync, and automated cleanup of older files.
\end{itemize}

\textbf{HouseFinder (Real Estate Analytics Platform)} $|$ Python, AWS, Pandas, Matplotlib, BeautifulSoup4
\begin{itemize}
    \item Developed a \textbf{data pipeline} to scrape, clean, and analyze real estate listings and neighborhood trends.
    \item Automated weekly delivery of \textbf{CSV + visualization reports} via AWS with persistent S3 artifacts.
\end{itemize}

\textbf{AutoJobApplier (Automation Tool)} $|$ Python, Selenium, Google Sheets API, BeautifulSoup4
\begin{itemize}
    \item Created an automation system that logs in, searches jobs, applies with stored data, and uploads resumes.
    \item Built an integrated \textbf{Google Sheets tracker} with a CSV fallback for monitoring application progress.
\end{itemize}

\textbf{SurvivalSprintHarvest (AI Simulation)} $|$ Java, Swing, OOP
\begin{itemize}
    \item Designed an \textbf{agent-based survival simulation} with adaptive foraging and energy-management strategies.
    \item Built a \textbf{real-time Swing visualizer} for debugging and analyzing emergent AI behaviors.
\end{itemize}

% =======================
% Skills
% =======================
\section{Skills}
\textbf{Languages}: Java, Python, C++, C, TypeScript, JavaScript, Swift, Kotlin, Dart, SQL, HTML/CSS\\
\textbf{Frameworks}: React, Node.js, Express, Flask, FastAPI, Jest\\
\textbf{Cloud/Tools}: AWS, GCP, Firebase, Docker, Git, Linux\\
\end{document}
